Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Move Table 1 earlier
Move Table 2 earlier
Clarify discussion of deadlines

% % When compared to conventional real-time systems, networked multimedia
% % deadlines are neither soft nor hard.
% Networked multimedia deadlines are unusual when compared to other real-time
% systems. They are simultaneously flexible and strict: flexible in that the exact
% value of the deadline is typically not important, provided it is of the right
% order-of-magnitude for the application, but strict in that any particular
% deadline provides a hard cut-off, after which the data is useless.
It is useful to distinguish between networked multimedia deadlines and
deadlines in conventional real-time systems. A multimedia deadline is neither
soft, since arrivals played after a deadline contribute to poor experience; nor
are deadlines hard, since occasional missed messages can be tolerated.

>>>>

Networked multimedia deadlines are unusual when compared to other real-time
systems. They are simultaneously flexible and strict: flexible in that the exact
value of the deadline is typically not important, provided it is of the right
order-of-magnitude for the application, but strict in that any particular
deadline provides a cut-off, after which the data arrives too late to be
rendered to the user (although, again, it is not entirely useless, since
it might be used to complete predictive coding state, improving the quality 
of frames decoded later).
